%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=1, top=1.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Qazi Fahim} % Your given name
\familyname{Farhan} % Your family name

% All information in this block is optional, comment out any lines you don't need
% \title{Curriculum Vitae}
\address{44/F/8-A,3rd floor B, Panthapath}{Dhaka 1215}
\mobile{+8801844675382}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{fahim.farhan@outlook.com}
\homepage{https://fahimfarhan.github.io/}{https://fahimfarhan.github.io/} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example

%\extrainfo{additional information}
% \photo[70pt][0.4pt]{me} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
% \quote{"Nothing is true, everything is permitted" - Assassin's creed}

%----------------------------------------------------------------------------------------

\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}

% \cventry{2015--2019}{B.Sc in Computer Science and Engineering(CSE)}{}{}{}{
%         % General description \newline{}%
% %     Detailed achievements:\\%
%     \begin{tabular}{  p{270pt}p{60pt}p{40pt}  }
% %     \textbf{Omr책de}                                    & \textbf{Utfall} & \textbf{Skala} \\ 
% %     \hline
%     Bangladesh University of Engineering and Technology    & CGPA                     & \textbf{2.73/4.00}   \\ 
%     \end{tabular}
% }

\cvitem{2015--2019}{\textbf{B.Sc in Computer Science and Engineering(CSE)}}
\cvitem{}{
    \begin{tabular}{  p{270pt}p{50pt}p{50pt}  }
        %     \textbf{Omr책de}                                    & \textbf{Utfall} & \textbf{Skala} \\ 
%     \textbf{Omr책de}                                    & \textbf{Utfall} & \textbf{Skala} \\ 
        %     \textbf{Omr책de}                                    & \textbf{Utfall} & \textbf{Skala} \\ 
        %     \hline
        Bangladesh University of Engineering and Technology    & CGPA                     & 2.73/4.00   \\ 
     \end{tabular}
}


% \cvitem{2014}{\textbf{H.S.C}}
% \cvitem{}{
%     \begin{tabular}{  p{270pt}p{50pt}p{50pt}  }
%         Notre Dame College, Dhaka    & GPA                     & \textbf{5.00/5.00}   \\ 
%     \end{tabular}
% }


% \cvitem{2012}{\textbf{S.S.C}}
% \cvitem{}{
%     \begin{tabular}{  p{270pt}p{50pt}p{50pt}  }
%         Govt. Laboratory High School, Dhaka    & GPA                     & \textbf{5.00/5.00}   \\ 
%     \end{tabular}
% }

\section{Standardized Test Scores}

\cvitem{09/12/2021}{\textbf{Graduate Record Examination (GRE)}}
\cvitem{}{
    \begin{tabular}{ p{92.5pt}p{92.5pt}p{92.5pt}p{92.5pt} }
        \centering \textbf{Total}  & \centering \textbf{Quantitative reasoning} & \centering \textbf{Verbal reasoning} &  \textbf{Analytical Writing} \\ 
    \hline
    \centering 311 &  \centering 160 &  \centering 148  & \centering 3  \\ 
    \end{tabular}
}

\cvitem{15/04/2022}{\textbf{International English Language Testing System (IELTS)}}
\cvitem{}{
    \begin{tabular}{ p{74pt}p{74pt}p{74pt}p{74pt}p{74pt} }
        \centering \textbf{Overall}  & \centering \textbf{Listening} & \centering \textbf{Reading} & \centering \textbf{Speaking} & \textbf{Writing} \\ 
    \hline
    \centering 7 &  \centering 7.5 &  \centering 7.5  & \centering 7 & \centering 6.5   \\ 
    \end{tabular}
}

\section{Work Experience}
\cvitem{May 2023--Present}{Software Developer, ShareTrip}
\cvitem{September 2019--April 2023}{Software Engineer, Ridmik Labs}

% \subsection{ \textbf{Professional projects} }
\cvitem{}{
    \textbf{Professional projects done at ShareTrips} 
}
\subsection{\href{https://play.google.com/store/apps/details?id=net.sharetrip&hl=en&gl=US}{ShareTrip: Book Flight \& Hotel}}
% \cvitem{Name}{\href{https://play.google.com/store/apps/details?id=ridmik.one&gl=US}{RidmikChat}}
\cvitem{Languages}{Kotlin}
% \cvitem{Framework}{Android}
\cvitem{Description}{Currently working on a marketplace feature. Ussers will be able to purchase products online through the app. \href{https://play.google.com/store/apps/details?id=net.sharetrip&hl=en&gl=US}{(Google Play Store link)}}



\cvitem{}{
    \textbf{Professional projects done at Ridmik Labs} 
}

\subsection{\href{https://play.google.com/store/apps/details?id=ridmik.one&gl=US}{RidmikChat}}
% \cvitem{Name}{\href{https://play.google.com/store/apps/details?id=ridmik.one&gl=US}{RidmikChat}}
\cvitem{Languages}{Kotlin, Java}
% \cvitem{Framework}{Android}
\cvitem{Description}{An android social media and chat application. I have worked on user profile page, news feed, image editor, video editor, fancy animations, etc features. \href{https://play.google.com/store/apps/details?id=ridmik.one&gl=US}{(Google Play Store link)}}

\subsection{\href{https://play.google.com/store/apps/details?id=ridmik.words}{Ridmik Dictionary}}
% \cvitem{Name}{\href{https://play.google.com/store/apps/details?id=ridmik.words}{Ridmik Dictionary}}
\cvitem{Languages}{Kotlin, Java}
% \cvitem{Framework}{Android}
\cvitem{Description}{An android dictionary application. I have implemented searching words, 
displaying word categories, splash cards, study page, MCQ, showing advertisements etc features.
\href{https://play.google.com/store/apps/details?id=ridmik.words}{(Google Play Store link)}}

\subsection{\href{https://play.google.com/store/apps/details?id=ridmik.news}{Ridmik News}}
% \cvitem{Name}{\href{https://play.google.com/store/apps/details?id=ridmik.news}{Ridmik News}}
\cvitem{Language}{Kotlin, Java}
% \cvitem{Framework}{Android}
\cvitem{Description}{An android news application that aggregates, and displays news. I have worked on the app settings, and displaying advertisements in the news feed.
\href{https://play.google.com/store/apps/details?id=ridmik.news}{(Google Play Store link)}}


\section{Teaching Experience}
\cvitem{Course Instructor}{ Made android app development videos on an educational platform named Interactive Cares. \href{https://play.google.com/store/apps/details?id=ridmik.news}{(Course link)} }
\cvitem{Home tutor}{ Worked as a home tutor. I taught math, physics, and chemistry to high school students. }

% \pagebreak

\section{Thesis}
\cvitem{Title}{\emph{Building Semantic Knowledge Graph using Twitter Data}}
\cvitem{Supervisor}{Dr. Muhammad Mashroor Ali}
\cvitem{Description}{In this thesis, we investigated how to build knowledge graph from 
                a very limited data source like Tweets. As the thesis progressed, 
                we faced some chalanges such as connecting external knowledge base, 
                choosing tentative candidates and disambiguating urls using various heuristic functions. 
                We have also used NLP tools (GATE developer) to analyze tweets and write necessary codes.
    \href{https://github.com/fahimfarhan/KnowledgeGraph}{(github link)}
 }

\section{Skills}
\cvitem{Programming Languages}{C, C++, Java, Kotlin, Julia, SQL, \LaTeX , Flex, Bison, Python, PHP, Javascript, C\#, Bash, Assembly 8086, MIPS } %{category 4}{XXX, YYY, ZZZ}
\cvitem{Frameworks}{Django, JavaFx, Android, Gradle, OpenGL}%{category 5}{XXX, YYY, ZZZ}
\cvitem{Operating System}{Debian 11 (testing), Linux Mint 20.3, Windows 11 }%{category 6}{XXX, YYY, ZZZ}
\cvitem{Databases}{Oracle, MySQL, PostgreSQL, OrientDB, SQLite }
\cvitem{Others}{Terminal, Git, Vim, Arduino Uno, Raspberry Pi, ATmega32}

\section{Online Judge/Contests}
% \cvitem{SnackDown 2019}{  \href{https://fahimfarhan.github.io/coding-creed-origins/certificates/fahimfarhan-SNCK19.pdf}{username: fahimfarhan, rank: 10364 (participation certificate link) } } 
\cvitem{Codeforces}{ \href{http://codeforces.com/profile/fahimfarhan}{username: fahimfarhan, Maximum Rating 1370 (profile link)} } 
\cvitem{LeetCode}{ \href{https://leetcode.com/fahimfarhan/}{username: fahimfarhan (profile link)} }
\cvitem{CodeChef}{ \href{https://www.codechef.com/users/fahimfarhan}{username: fahimfarhan, Maximum Rating 1589 (profile link) }  }
% \cvitem{vjudge}{ \href{https://vjudge.net/user/269707}{username: fahimfarhan (profile link) }  }
\cvitem{Google Kick Start 2019}{  \href{https://fahimfarhan.github.io/coding-creed-origins/certificates/fahimfarhan-Summary-Certificate-Kick-Start-2019.pdf}{username: fahimfarhan , highest position 1866 (participation certificate link) } } 
% \cvitem{Facebook Hacker Cup}{ Qualification round ranking 1805 }

% \section{Academic Major Projects}

\section{Major Academic or Personal Projects}

\subsection{ \href{https://github.com/fahimfarhan/NewsApp}{NewsApp} }
\cvitem{Language}{Kotlin, Java}
% \cvitem{Framework}{Android}
\cvitem{Description}{A simple android news app that demonstrates clean architecture. \href{https://github.com/fahimfarhan/NewsApp}{(github link)} }

\subsection{ \href{https://github.com/fahimfarhan/SimpleVideoEditor}{SimpleVideoEditor} }
\cvitem{Language}{ Java }
% \cvitem{Framework}{Android}
\cvitem{Description}{
An android video editor app that performs basic operations like crop, trim duration, apply filter, etc. \href{https://github.com/fahimfarhan/SimpleVideoEditor}{(github link)} }

\subsection{ \href{https://github.com/fahimfarhan/cancer-web-app}{cancer-web-app} }
\cvitem{Language}{Python}
% \cvitem{Framework}{Django}
\cvitem{Description}{A cancer patient management system made with Djando. \href{https://github.com/fahimfarhan/cancer-web-app}{(github link)} }

\subsection{ \href{https://github.com/fahimfarhan/rubics-cobe-solver}{rubics-cobe-solver} }
\cvitem{Language}{Assembly 8086}
\cvitem{Description}{An assembly 8086 code that can solve 2x2x2 rubics cube. \href{https://github.com/fahimfarhan/rubics-cobe-solver}{(github link)}  }

\subsection{ \href{https://github.com/fahimfarhan/Compiler}{Compiler} }
\cvitem{Language}{C, C++, Flex, Bison, Assembly 8086 }
\cvitem{Description}{ A simple C Compiler that takes a source program, creates tokens, an AST, and generates a corresponging 
 target program in Assembly x86. \href{https://github.com/fahimfarhan/Compiler}{(github link)} }

\subsection{ \href{https://github.com/fahimfarhan/OrientDB}{Database Project} }
\cvitem{Language}{Java, OrientDB database}
\cvitem{Description}{ A project to experiment with a NoSQL database named 
        OrientDB using a Twitter dataset. \href{https://github.com/fahimfarhan/OrientDB}{(github link)}  }

% \subsection{ \href{https://github.com/fahimfarhan/Smart-Locker}{Smart Locker}  }
% \cvitem{Language}{C}
% \cvitem{Description}{ A hardware project with ATmega32 microcontroller that uses sensors detect burglar. It also comes with an alarm and a password management system.
%                         \href{https://github.com/fahimfarhan/Smart-Locker}{(github link)} }

% \subsection{ \href{https://github.com/fahimfarhan/FileExplorerFx}{FileExplorerFx} }
% \cvitem{Language}{ Java, JavaFx }
% \cvitem{Description}{A simple file explorer that can be used to view, navigate through folders, and open files 
%         in a computer. Currenctly works with Windows. \href{https://github.com/fahimfarhan/FileExplorerFx}{(github link)} 
%   }

\subsection{ \href{https://github.com/fahimfarhan/Zaxon}{Zaxon} }
\cvitem{Language}{C, C++ }
\cvitem{Description}{A simple game where the player has to defeat an alien. \href{https://github.com/fahimfarhan/Zaxon}{(github link)} }

% \subsection{ \href{https://github.com/fahimfarhan/CodeIgniter-Blog}{CodeIgniter-Blog} }
% \cvitem{Language}{PHP, MySQL}
% \cvitem{Framework}{CodeIgniter}
% \cvitem{Description}{A simple basic blog where userss can log in and publish their thoughts. \href{https://github.com/fahimfarhan/CodeIgniter-Blog}{(github link)} }


\section{References}
\cvitem{}{Dr. Muhammad Masroor Ali}
\cvitem{}{Professor, Department of Computer Science and Engineering, Bangladesh University of Engineering and Technology, Dhaka-1205, Bangladesh }  % arguments 3 to 6 can be left empty
\cvitem{}{Phone: (880 2) 55167100 }
\cvitem{}{Email: mmasroorali@cse.buet.ac.bd }
\end{document}


%% end of file `template.tex'.
